---
title: "BellaBeat"
author: "Samrita"
date: "12/10/2021"
output: powerpoint_presentation
---


```{r setup, include= FALSE}
knitr::opts_chunk$set(echo = FALSE)

install.packages("tidyverse",repos =" http://cran.us.r-project.org ")
library(tidyverse)

install.packages("ggplot2")
library(ggplot2)

install.packages("reshape2", repos =" http://cran.us.r-project.org ") # for melt method
library(reshape2)


# analysis 1 : BMI vs Steps and Calories burnt
BMI_Analysis<-read.csv("CustomFiles/BMI_Analysis.csv")
str(BMI_Analysis)

steps_sleep_awake<-read.csv("CustomFiles/Weekday_steps_sleep_awake.csv")
str(steps_sleep_awake)

date_vs_others<-read.csv("CustomFiles/Date_vs_others.csv")
str(date_vs_others)

Intensity_Steps<-read.csv("CustomFiles/Steps_Intensity_hourly.csv")
Intensity_Steps_long<-Intensity_Steps %>% 
  pivot_longer(cols = c("TotalSteps", "TotalIntensity"), names_to = "Activity")
str(Intensity_Steps_long)

```

## R Markdown

Bellabeat, a high-tech manufacturer of health-focused products for women. 

Stakeholders:

1. Urška Sršen: Cofounder and Chief Creative Officer

2. Sando Mur: Cofounder and executive team member

3. Bellabeat marketing analytics team

## Problem statement
- Analyse smart device usage to gain insight.
- Provide high-level recommendations for Bellabeat’s marketing strategy

## Data Analysis tools

- Data cleaning, processing and analysis is done in BigQuery
- Data visualisation is done in R studio

## BMI vs Steps and Calories 

```{r analysis1}

ggplot(data = BMI_Analysis, aes(x= avg_BMI)) +
geom_line(aes(y = avg_Calories, color = 'Calories')) +
geom_line(aes(y = avg_steps, color = "Steps")) +
  labs(y = 'Calories and Steps count', x="Average BMI",caption = "**Plot has Average values of all users")

```

## BMI vs Calories burnt, active and sedentary minutes 
```{r analysis2}
#Analysis 2: BMI vs Calories burnt, active and sedentary minutes 

ggplot(data = BMI_Analysis, aes(x= avg_BMI)) +
  geom_line(aes(y = avg_Calories, color = 'Calories burnt')) +
  geom_line(aes(y = Avg_ActiveMinutes, color = "Active minutes")) +
  geom_line(aes(y = SedentaryMinutes, color = "Sedentary minutes")) +
  labs(y = 'Count',x="BMI",caption = "**Plot has Average values of all users")
```

## Average steps, sleep time vs days of week

```{r analysis3}
ggplot(data = steps_sleep_awake,) +
  geom_col(aes(x=reorder(as.character(Date_format),Avg_steps),y = Avg_steps, fill = Avg_sleep_mins))+
  labs(caption = "**Plot has Average values of all users",x="Weekdays",y=" Steps", fill="Sleep minutes")+
  theme(axis.text.x = element_text(angle=90))
```


## Average sleep time vs Sedentary minutes
```{r analysis4}
ggplot(data=date_vs_others,aes(x=Avg_sleep_mins))+
  geom_smooth(mapping = aes(y=Sedentary_Active_mins),method = 'loess',formula = y ~ x)

```


## Calories burnt vs Active minutes
```{r analysis5}
ggplot(data=date_vs_others,aes(x=Total_active_minutes))+
  geom_smooth(mapping = aes(y=Calories),formula = y ~ x,method = 'loess')+
  geom_point(mapping = aes(y=Calories))
```
  
## Activity time in a day
```{r analysis6}
ggplot(data = Intensity_Steps_long)+
  geom_bar(aes(x =reorder(Hours,value) , y = value, fill =Activity  ),stat="identity", position = "dodge")+
  labs(x="Day time",caption="**Average values taken for intensity and steps")
```

## Conclusion

- We notice only 24 % of users log their weight and BMI details. We must encourage them to enter the same regularly.
- Only 72% of people tracked their sleep on a daily basis. 
- Most users tend to get lazy on Sunday. 
- People looking to burn more calories should spend more time being active rather than sedentary which helps with good sleep.
- Many users like to walk in the morning and do high intensity activities in the evening or night. 


## Recommendation
- Marketing team should make the customers aware of the benefits of tracking their sleep.
- so Bellabeat can organize Sunday-Funday walking or running competitions among the users.
- Collaborate with local gyms for trial sessions for regular premium members. This can be used in     advertisements.
- Keep a weekly target of walk and high intensity activities, upon reaching refer users for free trial of bellabeat premium membership.